---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# farver

[![Travis-CI Build Status](https://travis-ci.org/thomasp85/farver.svg?branch=master)](https://travis-ci.org/thomasp85/farver)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/thomasp85/farver?branch=master&svg=true)](https://ci.appveyor.com/project/thomasp85/farver)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version-ago/farver)](http://cran.r-project.org/package=farver)
[![CRAN_Download_Badge](http://cranlogs.r-pkg.org/badges/farver)](http://cran.r-project.org/package=farver)
[![Coverage Status](https://img.shields.io/codecov/c/github/thomasp85/farver/master.svg)](https://codecov.io/github/thomasp85/farver?branch=master)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

The goal of `farver` is to provide very fast, vectorised conversion of colours
between different colour spaces, as well as provide fast colour comparisons 
(distance between colours). To this end it provides an interface to a modified 
version of the [ColorSpace](https://github.com/berendeanicolae/ColorSpace) C++ 
library developed by Berendea Nicolae.

## Installation
`farver` can be installed from CRAN using `install.packages('farver')`. The 
development version can be installed from Github using `devtools`:

```{r, eval=FALSE}
# install.packages('devtools')
devtools::install_github('thomasp85/farver')
```

## Use
The main functions of the package are`convert_colour()` with an interface very
much alike `grDevices::convertColor()`, and `compare_colour()` which allows you
to calculate the distance between colours using different metrics

### Conversion

```{r}
library(farver)

spectrum <- t(col2rgb(rainbow(10)))
spectrum

convert_colour(spectrum, 'rgb', 'lab')
```

### Comparison

```{r}
spectrum2 <- t(col2rgb(heat.colors(10)))

compare_colour(spectrum, spectrum2, 'rgb', method = 'cie2000')[1:6, 1:6]
```

## Supported colour spaces
`farver` currently supports the following colour spaces:

- CMY
- CMYK
- HSL
- HSB
- HSV
- CIE L*AB
- Hunter LAB
- LCH
- LUV
- RGB
- XYZ
- YXY

## Supported distance measures
`farver` supports the following colour distance metrics

- Euclidean
- CIE1976
- CIE94
- CIE2000
- CMC

## White References
`farver` allows you to set the white point for relative colour spaces, either
based on a standard illuminant (A-F series supported) or by specifying 
chromaticity coordinates or tristimulus values directly

## Benchmark
`farver` is faster than its `grDevices` counterpart but less so than it was at 
its first release, as the colour conversion in grDevices has been improved 
since.

```{r, message=FALSE}
library(ggplot2)
test <- matrix(runif(30000, min = 0, max = 255), ncol = 3)
timing <- bench::mark(
  farver = convert_colour(test, 'rgb', 'lab'),
  grDevices = convertColor(test, 'sRGB', 'Lab', scale.in = 255), 
  check = FALSE,
  iterations = 100,
  filter_gc = FALSE
)
plot(timing, type = 'ridge')
```

